# Clustering Assignment

```{r}
library(tidyverse)
library(tidymodels)
library(cluster)
library(factoextra)
library(dendextend)
```

```{r}
trucks <- read_csv("trucks-1.csv")
```

```{r}
ggplot(trucks, aes(x=Distance, y=Speeding)) +
  geom_point()
```

Question 1 - The data points are arranged in what appear to be four clusters.

```{r}
trucks_scaled = scale(trucks)
summary(trucks_scaled)
```

Question 2 - The maximum value of distance in the scaled data set is 3.1560.

```{r}
kmeans_recipe = recipe(~ Distance + Speeding, trucks) 

trucks_dummy = kmeans_recipe %>% 
  step_scale(all_numeric()) %>%
  step_center(all_numeric()) 

trucks_dummy = prep(trucks_dummy, trucks) #prepares the recipe

trucks_cleaned = bake(trucks_dummy, trucks)
```

```{r}
set.seed(64)
clusts = 
  tibble(k = 2) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```

```{r}
clusters = 
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
set.seed(64)
clusters = kmeans(trucks_cleaned, 2)

trucks = augment(clusters, trucks)
str(trucks)
```

```{r}
ggplot(trucks, aes(x=Distance, y=Speeding, color=factor(.cluster))) + geom_point()
```

Question 3 - Drivers with longer distances are in one cluster and drives with shorter distances are in another.

```{r}
set.seed(412)
clusts2 = 
  tibble(k = 1:8) %>%
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts2
```

```{r}
clusters2 = 
  clusts2 %>%
  unnest(cols = c(tidied))

assignments2 = 
  clusts2 %>% 
  unnest(cols = c(augmented))

clusterings2 = 
  clusts2 %>%
  unnest(cols = c(glanced))
```

```{r}
p1 = 
  ggplot(assignments2, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p1
```

```{r}
ggplot(clusterings2, aes(k, tot.withinss)) +
  geom_line() +
  geom_point()
```

Question 4 - A k of 4 is most appropriate.
Question 5 - A k of 4 is most apprpriate.

```{r}
set.seed(64)
clusters = kmeans(trucks_cleaned, 4)

trucks = augment(clusters, trucks)
str(trucks)
```

```{r}
p2 = 
  ggplot(assignments2, aes(x = Distance, y = Speeding)) +
  geom_point(aes(color = .cluster), alpha = 0.8) + 
  facet_wrap(~ k)
p2
```

```{r}
clust_trucks = kmeans(trucks_cleaned, centers = 4)

clust_trucks
```

```{r}
trucks = augment(clust_trucks, trucks)
head(trucks)
```

```{r}
ggplot(trucks, aes(x=Distance, y=Speeding, color=factor(.cluster))) + geom_point()
```

Question 6 - Short & Low, Long & High, Long & Low, Short & High (all of the above)